### 2014-11-13 tex/intro.tex
Commented out explanation of sound and complete--not needed for this audience

This combination of summary heap and lazy initialization
enable us to improve the efficiency of symbolic execution of heap
manipulating programs over state-of-the-art techniques.
Furthermore, the summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation relation
between states in GSE and states in the summary heap algorithm. In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, and, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.

@@

A preliminary implementation in Java Pathfinder (JPF) shows that in
general, that the heap summary algorithm improves over other
state-of-the-art techniques, and in some instances, the improvement is
remarkable: two-orders of magnitude reduction in running time. More
critically though, the heap summary enables the initialization of
larger more complex heaps than previously possible as shown in our
results.

>>>>

This combination of summary heap and lazy initialization
enable us to improve the efficiency of symbolic execution of heap
manipulating programs over state-of-the-art techniques.
Furthermore, the summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation
between states in GSE and states in the summary heap algorithm. 
\begin{comment}
In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, and, any property proved by
summary heaps can also be proved by GSE. Of course, both require a
bound on heap reference chains and loops.
\end{comment}

@@

A preliminary implementation in Java Pathfinder (JPF) shows that in
general, the heap summary algorithm improves over other
state-of-the-art techniques, and in some instances, the improvement is
remarkable: two-orders of magnitude reduction in running time. More
critically though, the heap summary enables the initialization of
larger more complex heaps than previously possible as shown in our
results.
